\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-15 draft.tex
finish empirical / evidence section

\textcolor{blue}{We `turn on' the parameters for interest groups for each vote according to the data from Maplight, which includes a listing of the votes for which each interest group took a position. This produces estimates for how ``friendly'' or ``unfriendly'' each legislator is with respect to each interest group, as well as the unpredictability of his/her voting behavior when matters affecting that group are considered. In a preliminary run of this model with just ten interest groups (out of over 450) in the 112th Congress displayed in Figure~\ref{fig:combined}, we find that the chemical industry has the lowest average uncertainty (sd = 0.229); this is lower than the total uncertainty measure that can be interpreted as the standard left-right measure in ideal point models (sd = 0.233). The median group in terms of uncertainty is manufacturing unions (sd = 0.253), while construction equipment faced the highest uncertainty (sd = 0.285).}

>>>>

Finally, we `turn on' the parameters for interest groups for each vote according to the data from Maplight, which includes a listing of the votes for which each interest group took a position. This produces estimates for how ``friendly'' or ``unfriendly'' each legislator is with respect to each interest group, as well as the unpredictability of his/her voting behavior when matters affecting that group are considered. In a preliminary run of this model with just ten interest groups (out of over 450) in the 112th Congress displayed in Figure~\ref{fig:combined}, we find that the chemical industry has the lowest average uncertainty (sd = 0.229); this is lower than the total uncertainty measure that can be interpreted as the standard left-right measure in ideal point models (sd = 0.233). The median group in terms of uncertainty is manufacturing unions (sd = 0.253), while construction equipment faced the highest uncertainty (sd = 0.285). This gives us a rich testing grounds for the model that is yet to be exploited.
